Automated Formal Synthesis of Digital Controllers for State-Space Physical Plants

### 2017-01-25 cav2017/cav2017.tex
form

Linear Time Invariant (LTI) models represent a broad class of dynamical systems
%modern embedded software, performing highly non-trivial control tasks,
with significant impact in numerous application areas as in 
the life sciences, robotics, and engineering~\cite{astrom1997computer,Franklin15}.
Synthesis of controllers for LTI models is broadly investigated, 
however the use of digital control architectures adds new challenges due to 
the effects of finite-precision arithmetic, time discretization, and quantization noise, which are typically introduced 
by Analogue-to-Digital (ADC) and Digital-to-Analogue (DAC) conversion.  
While research on digital control is well developed~\cite{astrom1997computer}, 
automated and sound control synthesis is challenging, 
particularly when the synthesis objective goes beyond classical stability or tracking requirements. 
Beyond stability, recently reachability tools have been developed \cite{FLD+11,Fre05}, however they have not been employed towards
control synthesis.
The problem of safety is an important one, since the synthesis of a stable controller does not ensure
that the system will not transitively visit an unsafe state which may result in an unrecoverable failure.

>>>>

Linear Time Invariant (LTI) models represent a broad class of dynamical
systems with significant impact in numerous application areas as in the life
sciences, robotics, and engineering~\cite{astrom1997computer,Franklin15}. 
Synthesis of controllers for LTI models is broadly investigated, however the
use of digital control architectures adds new challenges due to the effects
of finite-precision arithmetic, time discretization, and quantization noise,
which are typically introduced by Analogue-to-Digital (ADC) and
Digital-to-Analogue (DAC) conversion.  While research on digital control is
well developed~\cite{astrom1997computer}, automated and sound control
synthesis is challenging, particularly when the synthesis objective goes
beyond classical stability or tracking requirements.  Beyond stability,
recently reachability tools have been developed~\cite{FLD+11,Fre05}, however
they have not been employed towards control synthesis.  The problem of
safety is an important one, since the synthesis of a stable controller does
not ensure that the system will not transitively visit an unsafe state which
may result in an unrecoverable failure.
